---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# sfd - Space-Filling Designs

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/sfd)](https://CRAN.R-project.org/package=sfd)
[![R-CMD-check](https://github.com/topepo/sfd/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/topepo/sfd/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/topepo/sfd/branch/main/graph/badge.svg)](https://app.codecov.io/gh/topepo/sfd?branch=main)
<!-- badges: end -->

The goal of sfd is to make available a number of pre-optimized space-filling designs (SFDs) originating from [`https://www.spacefillingdesigns.nl/`](https://www.spacefillingdesigns.nl/) and the `mixtox` package. For the former, the original website offers no guarantee or license but does state that

> All these designs have been compared and the best designs are collected on this website. They can be downloaded for free and used in your specific simulation environment.

The available designs in this package are for experiments where the number of parameters ranges from two to 15 of types `"audze_eglais"`,  `"max_min_l1"`, `"max_min_l2"`, `"max_min_l1`", and `"uniform"`. 

The package has a function to see if a design is available (`sfd_available()`) and to retrieve it (`get_design()`).

The number of designs varies across type: 

```{r}
#| label: designs
#| echo: false
#| fig.height: 3
#| fig.width: 8

info <- tibble::tribble(
  ~num_param,          ~type, ~max_size,
          2L, "audze_eglais",      100L,
          2L,   "max_min_l1",      500L,
          2L,   "max_min_l2",      500L,
          2L,      "uniform",      150L,
          3L, "audze_eglais",      100L,
          3L,   "max_min_l1",       16L,
          3L,   "max_min_l2",      300L,
          3L,      "uniform",      150L,
          4L, "audze_eglais",      100L,
          4L,   "max_min_l1",        7L,
          4L,   "max_min_l2",      300L,
          4L,      "uniform",      150L,
          5L, "audze_eglais",      100L,
          5L,   "max_min_l1",        7L,
          5L,   "max_min_l2",      100L,
          5L,      "uniform",      150L,
          6L, "audze_eglais",      100L,
          6L,   "max_min_l1",        7L,
          6L,   "max_min_l2",      100L,
          6L,      "uniform",      150L,
          7L, "audze_eglais",      100L,
          7L,   "max_min_l1",        7L,
          7L,   "max_min_l2",      100L,
          7L,      "uniform",      150L,
          8L, "audze_eglais",      100L,
          8L,   "max_min_l1",        7L,
          8L,   "max_min_l2",      100L,
          8L,      "uniform",      150L,
          9L, "audze_eglais",      100L,
          9L,   "max_min_l1",        7L,
          9L,   "max_min_l2",      100L,
          9L,      "uniform",      150L,
         10L, "audze_eglais",      100L,
         10L,   "max_min_l1",        7L,
         10L,   "max_min_l2",      100L,
         10L,      "uniform",      150L,
         11L,      "uniform",      150L,
         12L,      "uniform",      150L,
         13L,      "uniform",      150L,
         14L,      "uniform",      150L,
         15L,      "uniform",      150L
  )

library(ggplot2)

ggplot(info, aes(num_param, max_size)) + 
  geom_point() + 
  geom_step(direction = "vh") + 
  facet_wrap(~ type, nrow = 1) +
  labs(x = "# Parameters", y = "Max. Grid Size") +
  theme_bw()
```

## Installation

The package can be installed from CRAN using

```r
install.packages("sfd")
```

You can install the development version of sfd like so:

```r
pak::pak("topepo/sfd")
```

## Code of Conduct

Please note that the sfd project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
